From DSL to HPC Component-Based Runtime:\\ A Multi-Stencil DSL Case Study

### 2015-07-29 WOLFHPC15/article/article.tex
fix compiler 29_07
fixing author
Add xspace
wolfhpc 29_07

\documentclass{acm_proc_article-sp}
\usepackage{tikz}
\usepackage{listings}
\usepackage{url}
\usepackage{cite}
%----------TIKZ
\usetikzlibrary{calc,arrows,shapes,automata,petri,positioning,decorations.markings,shadows}

\tikzset{
    use/.style={
    circle,draw=black,fill=black,scale=0.5,text=white
    },
    provide/.style={
    circle,draw=black,fill=white,scale=0.5
    },
    component/.style={
    rectangle,rounded corners=3pt,draw=black
    },
    dcomponent/.style={
    rectangle,rounded corners=3pt,dashed,draw=black
    },
    smallcp/.style={
    rectangle,rounded corners=3pt,draw=black,font=\tiny,
    },
    resource/.style={
    rectangle,rounded corners=3pt, dashed,draw=black,font=\tiny,
    },
    connection/.style={
    decoration={ markings,
      mark=at position 1 with {\node[fill=black,draw=black,circle,inner sep=2pt](conn){};}
      },
    postaction={decorate}
    },
    bconnection/.style={
    decoration={ markings,
      mark=at position 1 with {\node[fill=black,draw=black,circle,inner sep=2pt](conn){};}
      },
    postaction={decorate}
    },
    mpiconn/.style={
    decoration={ markings,
      mark=at position 0.99 with {\node[fill=black,draw=black,rectangle,,inner sep=2pt](mpi){};}
      },
    postaction={decorate}
    },
}
%-------------
\newenvironment{mydef}[1][Definition]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}

@@

\numberofauthors{2} 
\author{
% 1st. author
\alignauthor
Julien Bigot\\
       \affaddr{CEA, Maison de la Simulation}\\
       \affaddr{USR 3441}\\
       \affaddr{91191 Gif-sur-Yvette Cedex, France}\\
       \email{julien.bigot@cea.fr}
% 1st. author
\alignauthor
Helene Coullon\\
       \affaddr{INRIA}\\
       \affaddr{ENS Lyon, 46 Allee d'Italie}\\
       \affaddr{Lyon, France}\\
       \email{helene.coullon@inria.fr}
% 2nd. author
\and
\alignauthor
Christian Perez\\
       \affaddr{INRIA}\\
       \affaddr{ENS Lyon, 46 Allee d'Italie}\\
       \affaddr{Lyon, France}\\
       \email{christian.perez@inria.fr}
}

>>>>

\documentclass{acm_proc_article-sp}
\usepackage{tikz}
\usepackage{listings}
\usepackage{url}
\usepackage{cite}
\usepackage{subfig}
\usepackage{amsmath}
\usepackage{xspace}
%----------TIKZ
\usetikzlibrary{calc,arrows,shapes,automata,petri,positioning,decorations.markings,shadows}

\tikzset{
    use/.style={
    circle,draw=black,fill=black,scale=0.5,text=white
    },
    mpi/.style={
    rectangle,draw=black,fill=black,scale=0.8,text=white
    },
    provide/.style={
    circle,draw=black,fill=white,scale=0.5
    },
    component/.style={
    rectangle,rounded corners=3pt,draw=black
    },
    dcomponent/.style={
    rectangle,rounded corners=3pt,dashed,draw=black
    },
    smallcp/.style={
    rectangle,rounded corners=3pt,draw=black,font=\tiny,
    },
    resource/.style={
    rectangle,rounded corners=3pt, dashed,draw=black,font=\tiny,
    },
    connection/.style={
    decoration={ markings,
      mark=at position 1 with {\node[fill=black,draw=black,circle,inner sep=2pt](conn){};}
      },
    postaction={decorate}
    },
    bconnection/.style={
    decoration={ markings,
      mark=at position 1 with {\node[fill=black,draw=black,circle,inner sep=2pt](conn){};}
      },
    postaction={decorate}
    },
    mpiconn/.style={
    decoration={ markings,
      mark=at position 0.99 with {\node[fill=black,draw=black,rectangle,,inner sep=2pt](mpi){};}
      },
    postaction={decorate}
    },
}
%-------------
\newenvironment{mydef}[1][Definition]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}

\newcommand{\llc}{L\textsuperscript{2}C\xspace}

@@

\numberofauthors{3} 
\author{
% 1st. author
\alignauthor
Julien Bigot\\
       \affaddr{CEA, Maison de la Simulation}\\
       \affaddr{USR 3441}\\
       \affaddr{91191 Gif-sur-Yvette, France}\\ % remove cedex
       \email{julien.bigot@cea.fr}
% 1st. author
\alignauthor
Helene Coullon\\
       \affaddr{INRIA}\\
       \affaddr{ENS Lyon, 46 Allee d'Italie}\\
       \affaddr{Lyon, France}\\
       \email{helene.coullon@inria.fr}
% 2nd. author
\and
\alignauthor
Christian Perez\\
       \affaddr{INRIA}\\
       \affaddr{ENS Lyon, 46 Allee d'Italie}\\
       \affaddr{Lyon, France}\\
       \email{christian.perez@inria.fr}
}
